%-------------------------
% ATS-Friendly Resume - Pratim Bera
% Target: Google Frontend/Software Engineer
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.3in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% ATS-friendly section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Pratim Bera} \\ \vspace{4pt}
    \small
    \href{mailto:pratimbworkshop@gmail.com}{\underline{pratimbworkshop@gmail.com}} $|$
    \href{https://www.linkedin.com/in/pratimbera-464281241}{\underline{LinkedIn}} $|$
    \href{https://ptechroom.online/}{\underline{Portfolio}} $|$
    \href{https://github.com/Pratim05}{\underline{Github}}
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
\small{
Results-driven Frontend Developer with 1.5+ years of professional experience building scalable, responsive, and high-performance web applications using React.js, Next.js, TypeScript, and Tailwind CSS. Proven ability to deliver seamless user experiences through mobile-first design, component-driven architecture, and SSR/SSG optimization. Passionate about solving complex UI challenges and contributing to large-scale, high-impact products.
}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages:} JavaScript (ES6+), TypeScript, HTML5, CSS3 \\
    \textbf{Frameworks \& Libraries:} React.js, Next.js, Tailwind CSS, Redux, REST APIs \\
    \textbf{Tools \& Platforms:} Git, GitHub, VS Code, npm/yarn, Vercel \\
    \textbf{Concepts:} Responsive Web Design, Component Architecture, Performance Optimization, Cross-Browser Compatibility, Mobile-First Design, Web Accessibility (WCAG), SEO Best Practices \\
  }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Growth Panda}{Bengaluru, Karnataka, India (Remote)}
      {Frontend Developer}{Oct 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Engineered and maintained responsive, interactive web applications using \textbf{React.js, Next.js, and Tailwind CSS}, improving page load performance by optimizing component rendering and code splitting.}
        \resumeItem{Collaborated with UI/UX designers and backend engineers to implement pixel-perfect interfaces, ensuring cross-browser compatibility across Chrome, Firefox, Safari, and Edge.}
        \resumeItem{Developed reusable component libraries and design system elements, reducing UI development time by standardizing shared components across multiple product features.}
        \resumeItem{Implemented mobile-first, fully responsive layouts, ensuring seamless user experience across devices ranging from 320px to 4K resolutions.}
        \resumeItem{Integrated RESTful APIs and managed asynchronous data flows, improving data-fetching efficiency using Next.js server-side rendering (SSR) and static site generation (SSG).}
      \resumeItemListEnd

    \resumeSubheading
      {Euphoria GenX}{Kolkata, West Bengal, India}
      {MERN Stack Developer Intern}{Jul 2023 -- Nov 2023}
      \resumeItemListStart
        \resumeItem{Completed an intensive 5-month Industrial Training Program in \textbf{MERN Stack Development} (MongoDB, Express.js, React.js, Node.js), gaining hands-on experience in full-stack application development.}
        \resumeItem{Built and deployed full-stack web features including authentication flows, CRUD operations, and dynamic UI components using React.js and Node.js.}
        \resumeItem{Gained practical experience with RESTful API design, database schema modeling, and connecting frontend interfaces to backend services.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Personal Portfolio Website} $|$ \emph{Next.js, TypeScript, Tailwind CSS} $|$ \href{https://ptechroom.online}{\underline{Live Demo}}}{2024}
      \resumeItemListStart
        \resumeItem{Designed and developed a fully responsive developer portfolio using Next.js and Tailwind CSS, showcasing projects, skills, and professional experience with optimized performance (Lighthouse score 90+).}
        \resumeItem{Implemented SEO best practices including meta tags, Open Graph protocol, and structured data to maximize discoverability.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Dynamic Web Application} $|$ \emph{React.js, TypeScript, REST API}}{2023}
      \resumeItemListStart
        \resumeItem{Built a full-featured interactive web application with React.js, implementing state management, API integration, and component-driven architecture for a scalable and maintainable codebase.}
        \resumeItem{Applied performance optimization techniques including lazy loading, memoization, and debouncing to deliver a smooth user experience.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Global Institute of Science and Technology}{Haldia, West Bengal, India}
      {Bachelor of Computer Applications (BCA)}{Jul 2021 -- Jul 2024}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Data Structures \& Algorithms, Object-Oriented Programming, Database Management Systems, Computer Networks, Software Engineering, Web Technologies.}
        \resumeItem{Recipient of \textbf{Certificate of Academic Excellence}; active member of \textbf{National Service Scheme (NSS)}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS & CERTIFICATIONS-----------
\section{Achievements \& Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Certificate of Academic Excellence} -- Awarded for outstanding academic performance during BCA program. \\
    \textbf{National Service Scheme (NSS) Certificate} -- Recognized for community service and leadership contributions. \\
    \textbf{MERN Stack Industrial Training} -- Certified completion of professional-grade full-stack development training at Euphoria GenX.
  }}
\end{itemize}

%-------------------------------------------
\end{document}
